# UK Neuroinformatics publications

This page lists some recent publications in
[Computational Neuroscience and Neuroinformatics by UK researchers](http://neuroinformatics.org.uk).
It is not meant to be exhaustive but shows the breadth of
neuroinformatics work performed in the UK.

If you are part of the UK neuroinformatics community and wish to add a
publication to the list, just email Stephen Eglen the DOI and/or
pubmed reference.  Please do not send more than one or two papers so
that we maintain a diversity of publications from different research
groups.

```{r setup, include = TRUE, cache = FALSE,include=FALSE}
library(RefManageR)
file = "ukcnnn.bib"
BibOptions(check.entries = FALSE, style = "markdown", bib.style = "authoryear", cite.style = 'alphabetic', max.names=7)
bib = ReadBib(file, check="error")
```


### 2014 publications
```{r, results='asis',echo=FALSE}
bib[year="2014"]
```

### 2013 publications

```{r, results='asis',echo=FALSE}
bib[year="2013"]
```

### 2012 publications

```{r, results='asis',echo=FALSE}
bib[year="2012"]
```

## About this document

This document is created by some great [R](http://www.r-project.org)
software, namely [knitr](http://yihui.name/knitr/) and
[RefManageR](http://cran.r-project.org/web/packages/RefManageR/index.html).
The bibtex file is curated by [paperpile](http://paperpile.com).


To compile the document:

```{r,eval=FALSE}
require(knitr)
knit2html("nodepubs.Rmd")
```
